Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
removing comment.
s/rev/reverse/

\usepackage{amsmath}
\usepackage{url}

@@

\begin{quote}
sol: Can we use \verb|reverse| instead of \verb|rev| here?
\end{quote}

\begin{quote}
kazu: I used \verb|rev| just because it is short.
Actually I used \verb|reverse| once but it is overflowed
in the right hand side.
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
rev :: [a] -> [a]
rev = undefined
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
-- |
-- 'rev' @xs@ returns the elements of @xs@
-- in reverse order. @xs@ must be finite.
--
-- >>> rev [1,2,3]
-- [3,2,1]
--
-- prop> rev [] == rev []
-- prop> rev (xs ++ ys) == rev ys ++ rev (xs::[Int])
-- prop> rev (rev xs) == (xs::[Int])

rev :: [a] -> [a]
rev = undefined
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
describe "rev" $ do
  it "returns the first element in the last" $
    property $ \xs -> not (null xs) ==>
      head (rev xs) == last (xs :: [Int])

  it "returns the last element in the first" $
    property $ \xs -> not (null xs) ==>
      last (rev xs) == head (xs :: [Int])
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
rev :: [a] -> [a]
rev = foldl (flip (:)) []
\end{verbatim}
\end{quote}

>>>>

\usepackage{amsmath}
\usepackage{url}
\usepackage{alltt}

@@

@@

\begin{quote}
\small
\begin{verbatim}
reverse :: [a] -> [a]
reverse = undefined
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{alltt}
-- |
-- 'reverse' @xs@ returns the elements of @xs@
-- in reverse order. @xs@ must be finite.
--
-- >>> reverse [1,2,3]
-- [3,2,1]
--
-- prop> reverse [] == reverse []
-- prop> reverse (xs ++ ys) == reverse ys ++ \(\hookleftarrow\)
                               reverse (xs::[Int])
-- prop> reverse (reverse xs) == (xs::[Int])

reverse :: [a] -> [a]
reverse = undefined
\end{alltt}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
describe "reverse" $ do
  it "returns the first element in the last" $
    property $ \xs -> not (null xs) ==>
      head (reverse xs) == last (xs :: [Int])

  it "returns the last element in the first" $
    property $ \xs -> not (null xs) ==>
      last (reverse xs) == head (xs :: [Int])
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
reverse :: [a] -> [a]
reverse = foldl (flip (:)) []
\end{verbatim}
\end{quote}
